Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-24 krs-survey.tex
Filled sections on debugging and performance evaluation

@@

Ability to ``listen'' to the robot internal structures.

@@

\subsubsection{Is it fast enough? Scalability and responsiveness}
\label{sect|scalability}

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OMRKF & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
ARMAR/Tapas & KRS & Holzapfel, Waible \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\paragraph{Experiments} GSM has mostly been tested on table-top manipulation
and interaction tasks (a ``conversational helping hand'' as stated by the
authors) realized on a 7-DOF arm equipped with force feedback, cameras for blob
tracking and speech recognition (Sphinx4).

@@

\multirow{5}{0.7cm}[0.2cm]{\turn[1.5cm]{90}{\bf Expr. power}} & Logical formalism & Prolog & DL (OWL) & {\sc CycL} &  & ASP &  & & Horn clauses & TFS & \\
 & OWA/CWA & CWA & OWA & ? & ? & CWA & ? & ? & ? & ? & ? \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Space Representation & & & & & & & & ++  \\
 & Time representation & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & +++ & & & +  \\
 & Knowledge structure alteration & & ++ & & & ++ & & & & ++ &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & +++ & & &  \\
 & Presupposition accommodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & ++ & & & + \\
 & Learning & & + & & & & & & & ++ &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & +++ \par (semantic maps) & ++ (external amodal model) & & & & & ++ & ++ \\
 & instantiation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & + & + \\
 & ...with executive layers & & & & & & & + & ++ \\
 & NLP & & +++ (external) & & & +++ & & +++ & & +++ & \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & + & & & \\

>>>>

Knowledge representation systems do not mean anything to robots if they are
considered in isolation. This section proposes categories of features related
to the integration of the KRS into a larger software architecture that includes
perception routines, decision-making processes and actuation control.

We also mention some practical aspects of a real-world system, like
performances and monitoring tools that come along with the KRS.

@@

We have previously discussed (section~\ref{sect|grounding}) the principles of
the grounding process that aims at establishing and maintaining a connection
between percepts (and to a lesser extend, low-level actions) and symbols.

While every real-world cognitive robot need some kind of grounding, the actual
implementations lead to very different information flows.

The systems can be roughly split into two classes: \emph{passive} knowledge
repositories that process symbolic facts produced by lower-level sensori-motor
layers (\emph{push} flow); \emph{active} knowledge managers that directly query
(possibly by polling or on-demand) low-level layers.

This macroscopic distinction is however mostly a matter of defining the
frontiers of the KRS: some systems like KnowRob~\cite{Tenorth2009a} encompass
geometric reasoning layers that would be considered as external by other
systems like ORO~\cite{Lemaignan2010} that focus on the symbolic fact storage
and rely on a ecosystem of independent modules to provide and consume symbolic
knowledge.

\fxwarning{Some archi with the ability to ``listen'' to the robot internal
structures -> which ones?}

Other systems do not fit either in such a partition between active and passive
systems because they do not stand as independent modules but exist as diffuse,
\emph{ubiquitous} knowledge manipulation system~\cite{Jacobsson2008}, for
instance because they are primarily language~\cite{Ferrein2008, Sabri2011}.

@@

It is common to have knowledge representation systems at the heart of a
cognitive robotic architecture, and therefore KRS are easily ``burried'' in the
system.

At the same time, the symbolic model often provides a valuable synthetic view
on the whole state of the robot, furthermore easily understandable by the human
developer (the fact \concept{human1 issitting true} is easier to interpret than
the suite of relative coordinates of each joints of the human skeleton, as
provided by the human tracker, for instance).

That is the reason why having at hand good tools to trace and visualize at
run-time the evolution of the knowledge structure and contents, as well as
post-processing tools that can be run on the trace to precisely analyze the
cognitive behaviour of the robot, is useful.

\subsubsection{Evaluation of performances}
\label{sect|performances}

Benchmarks of symbolic systems for robots are notoriously hard to conduct for
several reasons: identifying good metrics for robotic experiments in general is
difficult because of the complex interactions between tenth of modules running
in parallel. Isolating the role of one specific component is thus hard.
Furthermore, knowledge representation systems are usually tightly connected to
numerous other modules, and the lack of standard API for knowledge services
makes it especially hard to switch between KRS to compare them. Also, because
service robots are design to act in rich, dynamic environments, possibly with
humans, building repeatable experiments is challenging.

Cognitive architectures and KRS in particular are consequently often
benchmarked with synthetic datasets (which leads to other issues: how to assess
the meaningfulness of the performance of a reasoner on an artificial
ontology?~\cite{Bail2010}) or \emph{toy} experiments~\cite{Chong2009} that do
not reflect real-world complexity.

While evaluating the performances of knowledge representation systems
themselves may be difficult, the cognitive performances of the robot as a whole
can be aptly evaluated through ``classical'' tests from the psychology (like
False-Belief experiments~\cite{Leslie2000} or the Token
test~\cite{DiSimoni1978}).

However, the performance evaluation of current tools is mostly qualitative and
scenario-specific (``did my system do the job for my task?''), and amongst the
surveyed KRS, only few systems proposes an evaluation of their performances
that could be compared to other system.

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OMRKF & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
ARMAR/Tapas & KRS & Holzapfel, Waibel \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\paragraph{Experiments} GSM has mostly been tested on table-top manipulation
and interaction tasks (a ``conversational helping hand'' as stated by the
authors) realized on a 7-DOF arm equipped with force feedback, cameras for blob
tracking and speech recognition (Sphinx4). Mavridis and Roy provide in addition
an in-depth analysis of the performance of GSM by the mean of a standard
psycholinguistic test, the \emph{Token test}~\cite{DiSimoni1978}.

@@

\multirow{5}{0.7cm}[0.2cm]{\turn[1.5cm]{90}{\bf Expr. power}} & Logical formalism & Prolog & DL (OWL) & {\sc CycL} &  & ASP &  & & Horn clauses & TFS & \\
 & OWA/CWA & CWA & OWA & ? & ? & CWA & ? & ? & ? & ? & ? \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Space Representation & & & & & & & & ++  \\
 & Time representation & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & +++ & & & +  \\
 & Knowledge structure alteration & & ++ & & & ++ & & & & ++ &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & +++ & & &  \\
 & Presupposition accommodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & ++ & & & + \\
 & Learning & & + & & & & & & & ++ &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & +++ \par (semantic maps) & ++ (external amodal model) & & & & & ++ & ++ \\
 & instantiation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & + & + \\
 & ...with executive layers & & & & & & & + & ++ \\
 & NLP & & +++ (external) & & & +++ & & +++ & & +++ & \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & + & & +++ (Token test) & & & \\
